### 2014-03-15 src/paper.Rnw
Fix space requirements
update

o.stats.sel.xop$scope  <- 'op'
o.stats.sel.xop$sampling  <- gsub('_per_op','',gsub('OP[.]1x','1/', o.stats.sel.xop$operator))
r.stats.sel.xop$scope  <- 'op'
r.stats.sel.xop$sampling  <- gsub('_per_op','',gsub('OP[.]1x','1/', r.stats.sel.xop$operator))

@@

<<analysis, child='analysis.Rnw'>>=
@
<<results, child='results.Rnw'>>=
@
<<results, child='discussion.Rnw'>>=
@
<<threats, child='threats.Rnw'>>=
@
<<conclusion, child='conclusion.Rnw'>>=
@
\FloatBarrier

>>>>

o.stats.sel.xop$scope  <- 'operator'
o.stats.sel.xop$sampling  <- gsub('_per_op','',gsub('OP[.]1x','1/', o.stats.sel.xop$operator))
r.stats.sel.xop$scope  <- 'operator'
r.stats.sel.xop$sampling  <- gsub('_per_op','',gsub('OP[.]1x','1/', r.stats.sel.xop$operator))

@@

<<analysis, child='analysis.Rnw'>>=
@
<<results, child='results.Rnw'>>=
@
<<results, child='discussion.Rnw'>>=
@
<<threats, child='threats.Rnw'>>=
@
<<conclusion, child='conclusion.Rnw'>>=
@
%\FloatBarrier
\clearpage
